\bf Drift Removal for Time Series Data Using Quantile Trend Filtering

### 2019-01-08 Manuscript/detrendify_JCGS.tex
introduction updates, timing experiments

>>>>

	There have been a number of occasions when researchers have sought to estimate the trend in the quantiles of a random variable over time or another co-variate given noisy observations of that variable. \cite{nychka1995nonparametric} estimated smooth quantile curves of friction profiles of syringes in order to automate their quality assessment procedures. \cite{Ning2014} proposed a method for separating chromatogram peaks from the smooth baseline and noise present in the measurements. \cite{brantley2014mobile} examined air pollutant measurements collected using a monitoring vehicle and proposed using a smooth baseline trend as an estimate of regional background pollution. We are interested in the problem posed by \cite{thoma2016south} concerning low-cost air pollutant sensors. Researchers at the U.S. Environmental Protection Agency have built prototypes of low-cost sensors that provide an un-calibrated measure of volatile organic compounds (VOCs) and hazardous air pollutants (HAPs) at a 1 second time resolution. To reduce cost and power consumption, the temperature and relative humidity of the air presented to the photoionization detectors (PIDs) is not controlled. A result the output signal exhibits a slowly varying baseline drift (minutes to hours). The purpose of these sensors is to protect the fenceline of industrial facilities by detecting whether VOC emissions from a local source are present and providing wind and concentration data to help identify the source and speed repairs.
